% vim:ft=tex:
%
\documentclass[12pt]{article}

\usepackage{graphicx}
\usepackage{amsmath}
\title{progress
}
\author{gareths --- \texttt{gareths@mds041-OptiPlex-780}}

\begin{document}
\maketitle
\pagebreak
Hi Brett and Steve.\\\\
This is the progress I have made so far with estimating parameters using metropolis hastings. I have coded both a standard metropolis hastings into Matlab and c. I have then coded a simulated Annealing algorithm into Matlab. The simulated annealing algorithm as far as I can tell is much more successful than the standard metropolis hastings. I have had to play around a bit with how to test the closeness of fit for the likelihood functions in the algorithms. I will hopeful explain my reasoning alright for each one. The next step I think is to take the Simulated annealing algorithm to an MPI code and then to GPU. \\

The MPI code will simply allow a comparison between a serial algorithm on a CPU to a multi-threaded implementation. To do this I don't think will be too difficult. Just for each temperature we send out multiple seed values and only take the best one for the next temperature iteration. I also want to take the standard metropolis to multithread for comparison. Since the two algorithms are extremely similar it would just be nice for comparison.\\

A concern for me is the estimation for the noise in the system. When I attempt to add noise to the output and try to fit a noise parameter to the output of the model filter I get a small value with the other parameters seemingly averaging out the noisy output. I'll include an image for what I mean here.
\section{Standard Metropolis Hastings}
Testing 1 2 3 how this is changing this is changing  quickly $\alpha = \frac{\theta}{\chi}$
\section{Simulated Annealing }
testing 2
\end{document}

